TODO

### 2023-01-08 write-ups/cogsci23_paper/manuscript.Rmd
add figure of methods

#Data import constants
date_start=lubridate::ymd('2021-07-19')
fig_path=here("figs")
read_data_path <- "data/processed_data/joined_data/"
annotation_path <- "data/annotations"
model_path <- "code/models"

@@

# TODOs
redraft intro & add citations
add figs
consider rerunning wi_game bet flower with a mixed effect (was being slow, so didn't) and other models

redraft methods
write analysis
write discussion
abstract & front matter

@@

Needs more transition here.

@@

TODO do methods get pictures?

@@

## Data Acquisition
@mankewitz2021 had participants play a real-time coordination game in groups of three, implemented using Empirica [@almaatouqEmpiricaVirtualLab2020]. On each trial, each group saw a set of 6 flower images. Each participant could see the values for four of the flowers (represented as a colored bar), such that each flower's value was hidden from one participant. Players could coordinate and discuss using a chat box, and each selected a flower. If one player selected a flower, it was worth the shown reward; if multiple players collided and selected the same flower, they got a low reward instead. Thus, participants were incentivized to coordinate on selecting different flowers. The rewards earned over the course of game translated in a monetary bonus for the participants at the end of the game.

In *individual utility* games, each player earned points for the flowers they selected; in the *shared utility* games, the points earned were averaged together, and all players in a game got the same reward. This made for slightly different incentives; in an individual game, players want to maximize the rewards of flowers they select, and only care about avoiding collisions with other players' selections; in a shared game, players want their teammates to select different high reward flowers, and are indifferent on who selects the highest one.

Each game was assigned a color of flower (white, red, yellow, purple) and the flower images were drawn from a set of 12 for that color, so players saw the same flowers repeatedly across the game, in different combinations. Each game consisted of 24 trials. The use of different flowers of the same color was to create a situation where players needed to refer to the images but didn't have preset names for them in the context, and thus would need to collaboratively develop shared referring expressions.

@@

Following @Mankewitz2021 we only included games where players finished all 24 trials in the game. We only included games where participants had access ot the chat box (@Mankewitz2021 also had a no-chat baseline condition). This left us with `r d.games.final |> filter(condition=="Individual Utilities") |> nrow()` games in the Individual Utilities condition and `r d.games.final |> filter(condition=="Shared Utilities") |> nrow()` in the Shared Utilities Condition.

@@

We then embedded each of these referring expressions using SBERT cite! in order to compare between referring expressions in semantic space. We use cosine distance between embedding pairs as a measure of similarity between the corresponding referring expressions.

For the pairwise comparisons of utterances during the game, we take the similarities for utterances that are within 2 trials of each other (ex. an utterance from trial 10 is compared with utterances from trials 8,9,10,11,12). We do this because different flowers were shown to different groups on different trials. This width is a compromise between having enough pairs of utterances and still being able to treat them as coming from one time point in the game.

@@

## Reduction of referring expressions
```{r wordcount, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Amount of words produced in referring expressions across trial in games in both conditions. A: Total words of referring language per game per trial. B: Words in each reference expression by trial. C: Total number of reference expressions per game per trial.", fig.height=2, fig.width=7}

@@

Consistent with the results from dyadic iterated reference games, the amount of referring language decreases over the course of the game. As shown in Fig @ref(fig:wordcount)A, the number of words of referring language decreases across the game in both conditions. This is due to the individual referring expressions getting shorter (@ref(fig:wordcount)B), while the total number of referring epxressions remains that same (@ref(fig:wordcount)C).

@@

```{r during, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Cosine similarities between SBERT embeddings of utterances produced within 2 trials of each other. Utterances were paired with other utterances from different games; from the same game, but a different utterer speaker; or from the same speaker (vertical panels). Utterances were either in reference to different flowers or both in reference to the same flower (horizontal panels).", fig.height=4, fig.width=10, out.width="100%"}
flower_all|> 
  filter(later-earlier<3) |> 
  mutate(distance=case_when(
    player1==player2 ~ "Same Person",
    game1==game2 ~ "Same Game",
    T ~ "Different Games"),
    same_flower=ifelse(ref1==ref2, "Same Flower", "Different Flowers")
  ) |> 
ggplot( aes(x=later,y=sim,color=condition))+     
  stat_summary(aes(group=str_c(color,condition), color=condition),fun.data = "mean_cl_boot", position = position_dodge(width=.3), alpha=.3, geom="point")+
  geom_smooth(formula=y~poly(x,2))+facet_grid(same_flower~distance)+theme(legend.position="bottom", legend.title=element_blank())+
        scale_x_continuous(limits=c(1,24), breaks=c(6,12,18,24))+
        scale_color_brewer(palette="Dark2")+
  labs(x="Trial Number", y="Cosine Similarity")+
  guides(color = guide_legend(override.aes = list(linetype = NA, alpha=1, fill=NA, size=5) ) )

@@

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
                aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                       caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

>>>>

#Data import constants
date_start=lubridate::ymd('2021-07-19')
fig_path=here("write-ups/cogsci23_paper/figs")
read_data_path <- "data/processed_data/joined_data/"
annotation_path <- "data/annotations"
model_path <- "code/models"

@@

@@

Needs more transition here. 
```{r interface, fig.env = "figure*", fig.pos = "t!", fig.width=6, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Player interface. Panel A shows the selection phase, where each participant sees 6 flowers, 4 with value bars. Panel B shows the feedback stage, after all players have selected. When multiple players select the same flower, they recieve a lower value rather than what is shown.  \\label{interface}", cache=FALSE}

selection <- png::readPNG(here(fig_path, "selection.png"))

feedback <- png::readPNG(here(fig_path, "feedback.png"))

a <- ggdraw() + draw_image(selection)
b <- ggdraw()+draw_image(feedback)

plot_grid(a,b, labels="AUTO")
```

@@

@@

## Data Acquisition
As described in @mankewitz2021, participants played a real-time coordination game in groups of three, implemented using Empirica [@almaatouqEmpiricaVirtualLab2020]. On each trial, each group saw a set of 6 flower images (Figure \ref{interface}A) . Each participant saw the values for four of the flowers (represented as a colored bar), such that each flower's value was hidden from one participant. Players could coordinate and discuss using a chat box before each selected a flower. If one player selected a flower, it was worth the shown reward; if multiple players collided and selected the same flower, they each got a lower reward instead (Figure \ref{interface}B). This incentivized participants to communicate about the flowers in order to coordinate on selecting differenct flowers. The rewards earned over the course of game translated in a monetary bonus for the participants at the end of the game.

In *individual utility* games, each player earned points for the flowers they selected; in the *shared utility* games, the points earned were averaged together, and all players in a game got the same reward. This made for slightly different incentives; in an individual game, players wanted to maximize the rewards of flowers they selected, and only cared about avoiding collisions with other players' selections; in a shared game, players wanted their teammates to select different high reward flowers, and were indifferent on who selected the highest one.

Each game was assigned a color of flower (white, red, yellow, purple) and the flower images were drawn from a set of 12 for that color, so players saw the same flowers repeatedly across the game, in different combinations. Each game consisted of 24 trials. The use of different flowers of the same color created situations where players did not have established names for the flowers in context and needed to develop shared referring expressions to clearly communicate with their partners.

@@

## Exclusions 
Following @mankewitz2021 we only included games where players finished all 24 trials in the game. We only included games where participants had access tt the chat box (@mankewitz2021 also had a no-chat baseline condition). This left us with `r d.games.final |> filter(condition=="Individual Utilities") |> nrow()` games in the individual utilities condition and `r d.games.final |> filter(condition=="Shared Utilities") |> nrow()` in the shared utilities Condition.

@@

We embedded each of the extracted referring expressions using SBERT [@reimers2019], and used cosine distance between embedding pairs as a measure of similarity between the corresponding referring expressions.

For the pairwise comparisons of utterances during the game, we took the similarities for utterances that were within 2 trials of each other (ex. an utterance from trial 10 was compared with utterances from trials 8,9,10,11,12). Presentation of flowers was randomized, so different groups saw different flowers combinations on the same number trial. The width of the comparison window was a compromise between having enough pairs of utterances while still being able to treat them as coming from one time point in the game.

@@

## Reduction of referring expressions
```{r wordcount, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Amount of words produced in referring expressions across trial in games in both conditions. A: Total words of referring language per game per trial. B: Words in each reference expression by trial. C: Total number of reference expressions per game per trial. \\label{wordcount}", fig.height=2, fig.width=7}

@@

Consistent with the results from dyadic iterated reference games, the amount of referring language decreases over the course of the game. As shown in Figure \ref{wordcount}A, the number of words of referring language decreases across the game in both conditions. This is due to the individual referring expressions getting shorter (Figure \ref{wordcount}B), while the total number of referring expressions remains that same (Figure \ref{wordcount}C).

@@

```{r during, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Cosine similarities between SBERT embeddings of utterances produced within 2 trials of each other. Utterances were paired with other utterances from different games; from the same game, but a different utterer speaker; or from the same speaker (vertical panels). Utterances were either in reference to different flowers or both in reference to the same flower (horizontal panels). \\label{during}", fig.height=4, fig.width=10, out.width="100%"}
flower_all|> 
  filter(later-earlier<3) |> 
  mutate(distance=case_when(
    player1==player2 ~ "Same Person",
    game1==game2 ~ "Same Game",
    T ~ "Different Games"),
    same_flower=ifelse(ref1==ref2, "Same Flower", "Different Flowers")
  ) |> 
ggplot( aes(x=later,y=sim,color=condition))+     
  stat_summary(aes(group=str_c(color,condition), color=condition),fun.data = "mean_cl_boot", position = position_dodge(width=.3), alpha=.3, geom="point")+
  geom_smooth(formula=y~poly(x,2))+facet_grid(same_flower~distance)+theme(legend.position="bottom", legend.title=element_blank())+
        scale_x_continuous(limits=c(1,24), breaks=c(6,12,18,24))+
        scale_color_brewer(palette="Dark2")+
  labs(x="Trial Number", y="Cosine Similarity")+
  guides(color = guide_legend(override.aes = list(linetype = NA, alpha=1, fill=NA, size=5) ) )

@@
